---
title: "cFu_SOP_20250501"
format: html
editor: visual
---

## **Standard Operating Procedure (SOP) for Processing TaqMan and CFU Count Data**

#### I. Analyze and Process TaqMan Data

1.  Standard curve in QuantStudio

2.  Export TaqMan results as a csv

3.  Copy the Sample column, use formula below to extract unique values to build the CFU Count **=UNIQUE(A2:A1000)**

4.  Name the TaqMan document as follows and save in cFu folder

5.  **\[Project\]\_\[CollectedBy\]\_\[YYYYMMDD\]\_\[RawTaq\].csv**

6.  Name the CFU Count document as follows and save in the cFu folder (add the counts later)

7.  **\[Project\]\_\[CollectedBy\]\_\[YYYYMMDD\]\_\[RawCount\].csv**

8.  Load required packages and load the RawTaq data into R

    ```{r}
    library(dplyr)

    library(ggplot2)

    library(scales)

    dat_Taq <- read.csv("path_to_RaqTaq.csv")
    ```

9.  Filter the data frame and calculate CFU_TaqMan for the experiment

    ```{r}
    dat_Taq <- dat_Taq %>%
      filter(
        Task == "Unknown", # Choose uknowns only, no controls
        !is.na(Sample), # Cleanup to remove empty wells if present
        grepl("x", Sample) # Keep only samples containing "x"
      ) %>%
      mutate(
        Quantity = ifelse(is.na(Quantity), 0, as.numeric(Quantity)), # If Cq is NA, assuming 0 DNA
        CFU_TaqMan = (Quantity / 0.00478) / 0.002 / (20 / 520) #pg DNA to CFU, to 2µL to 1mL, account for sample dilution, in this case 20 µL added to 500 µL PBS
      )
    ```

10. Add metadata and rename

```{r}
cFu_XX_YYYYMMDD_Taq <- dat_Taq %>%
  mutate(Date_Collected = "YYYYMMDD", Collected_By = "XX")

```

II\. Format and Analyze CFU Plate Count Data

1.  Use the RawCount file to add recorded counts in the following format

    **Sample, NX, NX.1, save the csv**

2.  Load packages and load data frame into R

    ```{r}
    library(dplyr)
    library(ggplot2)
    library(scales)
    library(tidyr)
    library(stringr)

    dat_Count <- read.csv("path_to_RawCount.csv")
    ```

3.  Pivot longer and calculate CFU_Count values

    ```{r}
    dat_Count <- dat_Count %>%
      mutate(
        Dilution_N = as.numeric(str_extract(Dilution, "(?<=N)\\d+")),
        CFU_Count = case_when(
          !is.na(Dilution_N) & Dilution_N >= 0 & Dilution_N <= 6 ~ Count * 10^Dilution_N * 20,
          TRUE ~ NA_real_
        )
      )
    ```

4.  Rename

    ```{r}
    cFu_XX_YYYYMMDD_Count <- dat_Count %>%
      mutate(Date_Collected = "YYYYMMDD", Collected_By = "XX")
    ```

5.  Add metadata from the sample submission sheet in this precise order

    ```{r}
    		cFu_XX_YYYYMMDD_Count <- cFu_XX_YYYYMMDD_Count %>%
    		  mutate(
    		    Date_Collected = "YYYYMMDD",
    		    Collected_By = "XX",
    		    Experiment_ID = "Adoptive_transfer_sort",
    		    Date_Plated = "Wednesday,_October_16,_2024",
    		    Date_Read = "Tuesday,_November_12,_2024",
    		    MTB_Strain_Type = "Erdman",
    		    Strain_Modifications = "none",
    		    Infection_Route = "aerosol",
    		    Mouse_Type = "SP140-/-",
    		    Treatment = "none",
    		    Organ_Tissue = "Lung",
    		    Sample_Storage = "4C_overnight",
    		    Preprocessing = "Digested_with_LibTM_DNase",
    		    Tissue_Homogenization_Method = "GentleMACS",
    		    Timepoint_dpi = 25,
    		    Log_Dilution_Factor = NA,
    		    Media = "7H11",
    		    Media_Additive = "none",
    		    Plate_Type = "24_well",
    		    Spreading_Method = "none",
    		    Total_Plates = 11,
    		    Number_of_Replicates = 3,
    		    Volume_Per_Plate_uL = 20
      )
    ```

## 
